Supplementary Information 1

### 2025-04-14 MS2_Krill.Rmd
adding numbers section off

@@

>>>>

We comparethe time series of differente population variables for Antarctic krill under most significant models in this analysis; a reference model without environmental or predator data and an alternative model that incorporates both environmental and predator information. Total biomass estimates remain relatively stable across both scenarios until around 2010. From that point onward, both models show a marked increase in biomass, although the reference model predicts higher values than the ecosystem-informed model, particularly during the final assessment years (2018–2020). Recruitment at age 0 exhibits strong variability over time. This is coincidence with [REF]. While both models show similar patterns, the reference model tends to estimate higher recruitment peaks, especially in recent years. Finally, spawning biomass (SpawnBio) follows trends similar to total biomass. Both models show a gradual increase after 2010, but the reference model again yields higher values in recent years.

@@

Population variables: Overall, the inclusion of ecosystem and predator data (s1.4) results in more conservative estimates of biomass, recruitment, and spawning stock, suggesting that ecosystem-informed models may provide a more precautionary and ecologically realistic basis for krill stock assessment and management.

### 2025-04-14 index.Rmd
adding numbers section off

---
title: "Supplementary Information 1"
subtitle: "Assessing ecosystem effects on the stock productivity of Antarctic Krill (*Euphausia superba*): An Integrated modeling perspective"
author: "Mardones, M; Jarvis Mason, E.T.; Pinones, A.;  Santa Cruz, F.; Cárdenas, C.A"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: SA_krill.bib
#csl: apa.csl
csl: icesjournal.csl
link-citations: yes
linkcolor: blue
output:
  html_document:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r mapa, out.width='50%', fig.show='hold',fig.cap="Subarea 48.1 and management strata considered in the spatio-temporal analysis of intrinsic productivity of Krill (BS=Brainsfield Strait, EI= Elephant Island, Gerlache= Gerlache strait, JOIN= Joinville Island, SSWI= South West)"}
knitr::include_graphics('Figs/481.png')
```

@@

```{r fig.height=8, fig.width=6}
par(mfrow=c(2,1), mar=c(5,4,2,1))
SSplotData(base.model1.1, 
           subplots = 1,
           pheight = 15)

@@

>>>>

---
title: "Supplementary Information 1"
subtitle: "Assessing ecosystem effects on the stock productivity of Antarctic Krill (*Euphausia superba*): An Integrated modeling perspective"
author: "Mardones, M; Jarvis Mason, E.T.; Pinones, A.;  Santa Cruz, F.; Cárdenas, C.A"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: SA_krill.bib
#csl: apa.csl
csl: icesjournal.csl
link-citations: yes
linkcolor: blue
output:
  bookdown::html_document2:
    keep_md: true
    toc: true
    toc_deep: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    fontsize: 0.9em
    linestretch: 1.7
    html-math-method: katex
    self-contained: true
    code-tools: true
    number_sections: false
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r mapa, out.width='50%', fig.cap="Subarea 48.1 and management strata considered in the spatio-temporal analysis of intrinsic productivity of Krill (BS=Brainsfield Strait, EI= Elephant Island, Gerlache= Gerlache strait, JOIN= Joinville Island, SSWI= South West)"}
knitr::include_graphics('Figs/481.png')
```

@@

```{r fig.height=10, fig.width=6}
par(mfrow=c(2,1), mar=c(5,4,2,1))
SSplotData(base.model1.1, 
           subplots = 1,
           pheight = 15)

@@

### Code Repository

The repository with code to replicate this analysis can be found in this [GitHub author link](https://github.com/MauroMardones/SA_Krill)
